Asymmetric relationships and their effects on coexistence: Supporting information

### 2023-02-26 paper/Paper.Rnw
finished editing REsults for now, though will come back to it again after Jasmin finishes modifying the diatom figures

%the log-normal fecundities version
The \emph{log-normal fecundities lottery model} used $B_i = \exp(\sigma+\mu_i b_i)$,
and therefore had parameters $\sigma$, $\mu_1$ and $\mu_2$ in addition to the death rate parameter $\delta$
(Introduction) that both versions of the lottery model used. The parameter $\sigma$ is the variance of the
log-fecundities and $\mu_i$ is the mean log fecundity for species $i$.

%the beta fucundities version
The \emph{beta-fecundities lottery model}
used $B_i = \eta_i F_\beta^{-1} \circ \varphi(b_i)$, where $\varphi$ is the CDF of the standard normal
distribution and $F_\beta$ is the CDF of a beta distribution 
with shape and scale parameters $0.5$ (probability density function proportional to $x^{-05}(1-x)^{-0.5}$ on
the unit interval). So the beta-fecundities model had parameters $\eta_1$, $\eta_2$ and $\delta$,
and produced fecundities with $U$-shaped, beta distributions between $0$ and $\eta_1$, for $B_1$, and
$\eta_2$, for $B_2$. The mean fecundity for species $i$ was $\eta_i/2$, and larger $\eta_i$ also 
corresponded to more variable fecundities for species $i$. The parameter $\eta_i$ represents the upper
bound on what fecundities could occur for species $i$.

@@

%Plotting shortcuts for the log-normal fecundities model
To explore, using the log-normal fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\mu_1$, $\mu_2$, $\sigma$ and $\delta$.
We labeled regions of the plot which corresponded to ATA rescue or exclusion, i.e., regions for which
GWR and GWR-$\Delta_i^{[EC]}$ had opposite signs.
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose GWR of the weaker competitor, species 1. 
Second, we showed that, for the log-normal fecundities
lottery model, none of the components of (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we plotted against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated noises (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we only generated plots 
for left-tail associated noise. For each combination of $\delta=0.2, 0.4, 0.6$
and $\mu_1-\mu_2=0,-0.5,-2,-4$,
we plotted the components of (\ref{eq:full_decomp}) against $\sigma$. 
%***DAN: Jasmin mentioned that she only used \delta=0.2, .4, .6 because of a comment Ellner made where he 
%said it was known that larger values of \delta made for very little storage effects. Read that comment 
%again and then write something here to jstify the choice. I think I can probably then delete the section of
%sup mat, mentioned in the commented text below, that talks about \delta=1.
%Mathematical simplications for the $\delta=1$ case make it straightforward to see that
%coexistence is impossible and that the case is relatively trivial (SI 
%section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations are in 
SI section \ref{SI-sect:efficient_computation}.

%Then a similar para for the beta-fecundity lottery model.
To explore, using the beta fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\eta_1$, $\eta_2$, and $\delta$,
again labelling regions corresponding to ATA rescue or exclusion.
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\eta_1 \leq \eta_2$. To understand coexistence, 
it was then sufficient to decompose GWR of the weaker competitor, species 1. 
Second, we showed that, for the beta fecundities
lottery model, none of the components of (\ref{eq:full_decomp}) depends independently on $\eta_1$ and $\eta_2$;
instead they depend only on $\eta_1/\eta_2$ (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we plotted against $\eta_1/\eta_2$. 
For each combination of $\delta=0.2, 0.4, 0.6$
and for left- and right-tail associated noise, we plotted 
the components of (\ref{eq:full_decomp}) against the upper bound ratio $\eta_1/\eta_2$. 
The simulation methods of \cite{Ellner_2019} were again used.
Computationally efficient means of performing these simulations are in 
SI section \ref{SI-sect:efficient_computation}.

@@

%***DAN: made it to here, 2023 02 03, 4:11 pm. Resume from here.

%***DAN: copy of goal from the Intro
%G2) To explore, using the simple lottery model, the relative magnitudes of the contributions to coexistence that come
%from ATAs compared to other, previously known mechanisms of coexistence; and to determine whether species may 
%sometimes coexist with ATAs but not without, or vice versa.

%G2 
To begin fulfilling goal G2 of the Introduction (to explore, using the lottery model, the relative magnitudes 
of the contributions to coexistence that come from ATAs compared to other mechanisms; and to see if ATA rescue 
or ATA exclusion can occur), Fig.
\ref{fig:fig3} shows that the ATA term of (\ref{eq:full_decomp}) often, but not always, has 
magnitude comparable to the magnitudes of other terms of the extended MCT decomposition. 
Magnitudes of $\Delta_i^{[EC]}$ tended to be larger, relative to the magnitudes of the 
other terms of (\ref{eq:full_decomp}), for smaller-magnitude differences between $\mu_1$ and 
$\mu_2$, i.e., for closer-to-equal competitors. 
In the $\mu_1=\mu_2$ case (panels a-d), for which the two species were equal 
competitors, storage effects (blue plus red
lines on Fig. \ref{fig:fig3}) were the only means by which coexistence could occur, and ATA effects
tended to be negative, weakening total storage effects.

%G3
Fulfilling goal G3 of the Introduction (to explore, using the lottery model, whether species
can coexist with ATAs, but not without, or vice versa), our results show that ATAs can, indeed, sometimes
make the difference between coexistence and exclusion: both ``ATA rescue'' and ``ATA
exclusion'' (see Methods) are possible.
For some of the panels on Fig. \ref{fig:fig3}, the GWR line falls between the ATA
line and the $x$ axis for some values of $\sigma$, e.g., see panel h. 
Such cases correspond to parameter combinations
for which the presence or absence of ATAs determine whether the species coexist or not. In the 
case of panel h, for values of $\sigma$ around $4$, 
species 1 is excluded with ATAs but the two species can coexist without ATAs. 
Fig. \ref{fig:fig4} highlights additional examples. Orange lines on Fig. \ref{fig:fig4}
represent GWR when the effects of ATAs are included, and blue lines are GWR when
the effects of ATAs are removed. These two lines frequently crossed the $x$ axis in 
different places, showing that both ATA rescue space and ATA exclusion space can be non-empty
subsets of our trait-difference space (see Methods). For the parameters we considered, 
both ATA rescue and exclusion were more common for larger values of $\sigma$.
ATA rescue appeared more likely for smaller $\delta$, whereas ATA exclusion appeared
more common for larger $\delta$. Although some bands of ATA rescue or exclusion on Fig.
\ref{fig:fig4} appear narrow, they nevertheless do occur, which means ATAs can mean the 
difference between coexistence and extirpation of one species in some cases.

%G4
Fulfilling goal G4 of the Introduction (to provide an empirical example of species coexistence 
which highlights the role ATAs can play), Fig. \ref{fig:fig5} and Fig. \ref{fig:fig6} 
show that ATA contributions to coexistence often have magnitudes comparable to the 
magnitudes of other terms of the extended MCT decomposition (Fig. \ref{fig:fig5}), and that 
ATA rescue occurs for many combinations of parameters for this system (Fig. \ref{fig:fig5},
but especially Fig. \ref{fig:fig6}).

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig3.pdf}
\caption{The contribution of ATAs to species coexistence is often meaningfully large compared to 
other components of the MCT decomposition. All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel, 
$\delta$ and $\mu_1-\mu_2$ 
are fixed at values specified in the margins, and GWR and components of the decomposition
are plotted against $\sigma$. The contribution of ATAs (red line) frequently 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line (orange) falls 
between the ATA line (red)
and the $x$ axis, indicating that, for those parameter values, ATAs make the difference between species
coexistence and exclusion of the weaker competitor. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3,5)}, so are not displayed. This plot uses $q_{ij}=1$. An 
analogous plot (SI Fig. \ref{SI-fig:fig3_alt}) was generated 
using $q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. Though results differed
in some details, main conclusions were the same. \label{fig:fig3}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig4.pdf}
\caption{ATAs can sometimes make the difference between species coexistence and exclusion of the weaker
competitor: both ``ATA rescue'' and ``ATA exclusion'' (see Methods) are possible. 
All panels show GWR, the ATA term of the extended MCT [$\Delta_i^{[EC]}$ in equation 
(\ref{eq:full_decomp})], and the difference of these quantities. 
For each panel, $\delta$ and $\sigma$ are fixed at values specified in the 
margins, and the three quantities are plotted against $\mu_1-\mu_2$ to isolate points in the
``trait-difference space'' corresponding to ATA rescue 
($\psi_{\text{ATA}}(\delta,\sigma) \setminus \psi_{\lnot\text{ATA}}(\delta,\sigma)$) 
or ATA exclusion ($\psi_{\lnot\text{ATA}}(\delta,\sigma) \setminus \psi_{\text{ATA}}(\delta,\sigma)$; 
see Methods). Values of $\mu_1-\mu_2$ for which GWR is positive but 
$\text{GWR}-\Delta_i^{[EC]}$ is negative correspond to ATA rescue (shaded yellow), whereas
values of $\mu_1-\mu_2$ for which GWR is negative but $\text{GWR}-\Delta_i^{[EC]}$ is positive 
correspond to ATA exclusion (shaded violet). Top panels also include domains
of ATA rescue or exclusion, but they were too narrow to be highlighted by shading and are
probably of minimal importance. 
Standard errors of plotted quantities were never greater than \Sexpr{round(se4,5)}, 
so are not displayed. The dashed red line on panel (l) corresponds to the parameters
used for Fig. \ref{fig:pedagog}. This plot uses $q_{ij}=1$. An analogous plot was generated 
using $q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$, but it looked exactly the same, by mathematical necessity (see SI section \ref{SI-sect:F4andqij}).}\label{fig:fig4}
\end{figure}

>>>>

%the log-normal fecundities version
The \emph{log-normal fecundities lottery model} used $B_i = \exp(\mu_i+\sigma b_i)$,
and therefore had parameters $\sigma$, $\mu_1$ and $\mu_2$ in addition to the death rate parameter $\delta$
(Introduction) that both versions of the lottery model used. The parameter $\sigma$ is the standard deviation of the
log-fecundities and $\mu_i$ is the mean log fecundity for species $i$.

%the beta fucundities version
The \emph{beta fecundities lottery model}
used $B_i = \eta_i F_\beta^{-1} \circ \varphi(b_i)$, where $\varphi$ is the CDF of the standard normal
distribution and $F_\beta$ is the CDF of a beta distribution 
with shape and scale parameters $0.5$ (probability density function proportional to $x^{-05}(1-x)^{-0.5}$ on
the unit interval). So the beta fecundities model had parameters $\eta_1$, $\eta_2$ and $\delta$,
and produced fecundities with $U$-shaped, beta distributions between $0$ and $\eta_1$, for $B_1$, and
$\eta_2$, for $B_2$. The mean fecundity for species $i$ was $\eta_i/2$, and larger $\eta_i$ also 
corresponded to more variable fecundities for species $i$. The parameter $\eta_i$ represents the upper
bound on what fecundities could occur for species $i$.

@@

%Plotting shortcuts for the log-normal fecundities model
To explore, using the log-normal fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\mu_1$, $\mu_2$, $\sigma$ and $\delta$.
We labeled regions of the plot which corresponded to ATA rescue or exclusion, i.e., regions for which
GWR and GWR-$\Delta_i^{[EC]}$ had opposite signs.
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose GWR of the weaker competitor, species 1. 
Second, we showed that, for the log-normal fecundities
lottery model, none of the components of (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we plotted against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated noises (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we only generated plots 
for left-tail associated noise.

For each combination of $\delta=0.2, 0.4, 0.6$ and $\mu_1-\mu_2=0,-0.5,-2,-4$,
we plotted the components of (\ref{eq:full_decomp}) against $\sigma$ for $\sigma$ ranging 
from $0$ to $7$. Some of 
the $\mu$ differences and $\sigma$ values we considered were very unrealistic (see Results),
so we considered after plotting whether conclusions about the importance of ATAs depended 
on realistic values of parameters.
%***DAN: Jasmin mentioned that she only used \delta=0.2, .4, .6 because of a comment Ellner made where he 
%said it was known that larger values of \delta made for very little storage effects. Read that comment 
%again and then write something here to jstify the choice. I think I can probably then delete the section of
%sup mat, mentioned in the commented text below, that talks about \delta=1.
%Mathematical simplications for the $\delta=1$ case make it straightforward to see that
%coexistence is impossible and that the case is relatively trivial (SI 
%section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations are in 
SI section \ref{SI-sect:efficient_computation}.

%Then a similar para for the beta-fecundity lottery model.
To explore, using the beta fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\eta_1$, $\eta_2$, and $\delta$,
again labelling regions corresponding to ATA rescue or exclusion.
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\eta_1 \leq \eta_2$. To understand coexistence, 
it was then sufficient to decompose GWR of the weaker competitor, species 1. 
Second, we showed that, for the beta fecundities
lottery model, none of the components of (\ref{eq:full_decomp}) depends independently on $\eta_1$ and $\eta_2$;
instead they depend only on $\eta_2/\eta_1$ (SI section \ref{SI-SIsect:TheoryForLottery}). 
So we plotted against $\eta_2/\eta_1$.

For each combination of $\delta=0.2, 0.4, 0.6$
and for left- and right-tail associated noise, we plotted 
the components of (\ref{eq:full_decomp}) against the upper bound ratio $\eta_2/\eta_1$, using 
the fairly realistic range $1 \leq \eta_2/\eta_1 \leq 5$. 
The simulation methods of \cite{Ellner_2019} were again used.
Computationally efficient means of performing these simulations are in 
SI section \ref{SI-sect:efficient_computation}.

@@

%G2 
To begin fulfilling goal G2 of the Introduction (to explore, using the lottery model, the relative magnitudes 
of the contributions to coexistence that come from ATAs compared to other mechanisms; and to see if ATA rescue 
or ATA exclusion can occur), Fig.
\ref{fig:fig3} shows that, for the log-normal fecundities lottery model, 
the ATA term of (\ref{eq:full_decomp}) sometimes, but not always, has 
magnitude comparable to the magnitudes of other terms of the extended MCT decomposition. 
Magnitudes of $\Delta_i^{[EC]}$ tended to be larger, relative to the magnitudes of the 
other terms of (\ref{eq:full_decomp}), for smaller-magnitude differences between $\mu_1$ and 
$\mu_2$, i.e., for closer-to-equal competitors. 
In the $\mu_1=\mu_2$ case (panels a-c), for which the two species were equal 
competitors, storage effects ($\Delta_i^{[EC]}+\Delta_i^{[E\nat C]}$) 
were the only means by which coexistence could occur, and ATA effects
tended to be negative, weakening total storage effects. The ATA term 
was also often comparable in magnitude to the other terms of 
the decomposition (\ref{eq:full_decomp}) for the beta fecundities lottery model 
(Fig. \ref{fig:fig4}).

Our results also show that ATAs can make the difference between coexistence 
and failure of two species to coexist: both ``ATA rescue'' and ``ATA
exclusion'' (see Theory) are possible. Starting with the log-normal fecundities 
lottery model, for some of the panels on Fig. \ref{fig:fig3}, the GWR line falls between the ATA
line and the $x$ axis for some values of $\sigma$, e.g., see panel i.
Such cases correspond to parameter combinations
for which the presence or absence of ATAs determine whether the species coexist or not. In the 
case of panel i, for values of $\sigma$ around $6$, 
species 1 is excluded with ATAs but the two species can coexist without ATAs. 
Fig. \ref{fig:fig4} highlights additional examples using the beta fecundities lottery model.

For the log-normal fecundities lottery model, the ATA term from (\ref{eq:full_decomp}) tended
only to be comparable in magnitude to the other terms, and ATA exclusion or rescue tended only to
occur, for unrealistic parameters values; but ATA terms were large and ATA rescue and exclusion occurred
for realistic parameter values for the beta fecundities lottery model. For instance, the ATA in 
Fig. \ref{fig:fig3} was fairly 
small, compared to the other terms of (\ref{eq:full_decomp}), for values of $\sigma$ less than 
about $3$. And ATA rescue and exclusion also only occurred for $\sigma$ greater than about $3$.
The standard deviation of fecundity for species 1 when 
$\mu_1=0$ and $\sigma=3$ was greater than $8000$, so values of $\sigma$ greater than $3$ are 
probably unrealistic. Thus ATAs seem to be unimportant for coexistence
for the log-normal fecundities lottery model using realistic parameter values. However, 
all the $\eta_2/\eta_1$ ratio values we plotted were fairly realistic, corresponding to
upper-bound fecundities that were up to $5$ times higher for species 2 than for species 1. And 
the ATA term plotted in Fig. \ref{fig:fig4} was comparable in magnitude 
to the other components of (\ref{eq:full_decomp}) across the whole range of $\eta_2/\eta_1$ values
considered; and both ATA rescue and exclusion occurred for values of this ratio between $1$ and $2$.
Apparently the question of whether ATAs are important for realistic parameter values depends on model specifics.

%G4 ***DAN: Dan, this will have to be edited after Jasmin gets done editing the corresponding figures
Fulfilling goal G4 of the Introduction (to provide an empirical example of species coexistence 
which highlights the role ATAs can play), Fig. \ref{fig:fig5} and Fig. \ref{fig:fig6} 
show that ATA contributions to coexistence often have magnitudes comparable to the 
magnitudes of other terms of the extended MCT decomposition (Fig. \ref{fig:fig5}), and that 
ATA rescue occurs for many combinations of parameters for this system (Fig. \ref{fig:fig5},
but especially Fig. \ref{fig:fig6}).

@@

%***DAN: Jasmin, this figure looks really great. Here are a few minor things I would like to ask you to
%do to further optimize:
%1) Currently there are axis labels and numbers only on the bottom and left panels, which makes sense.
%But the axis tick marks needs to occur on all panels. I noticed that this would be an imporvement
%when I found myself wanting to see where the ATA line was between the x axis and the GWR line, but it was 
%a little hard to see where the x axis was becuase there were no tick marks. It is possible to have tick marks
%but no numbers of labels in R, and that's what we need here.
%2) The font of the x axis label, "log fcundity standard deviation, \sigma" seems slightly different from the 
%other textual labels. Can you please make it consistent? Perhaps it is not bold and the others are bold, or 
%something.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLLN.pdf}
\caption{The contribution of ATAs to species coexistence was often meaningfully large compared to 
other components of the MCT decomposition for the log-normal fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel, 
$\delta$ and $\mu_1-\mu_2$ 
are fixed at values specified in the margins, and GWR and components of the decomposition
are plotted against $\sigma$. The contribution of ATAs ($\Delta_i^{[EC]}$) frequently 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs 
make the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3,5)}, so are not displayed. This plot uses $q_{ij}=1$. An 
analogous plot (SI Fig. \ref{SI-fig:fig3_alt}) was generated 
using $q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. Though results differed
in detail, main conclusions were the same. \label{fig:fig3}}
\end{figure}

%***DAN: Jasmin, panel labels(a, b, c, etc.) need to be added. Please use the same format for these labels
%as you do in the other figures.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLB.pdf}
\caption{The contribution of ATAs to species coexistence was often meaningfully large compared to 
other components of the MCT decomposition for the beta fecundities lottery model.
All panels show GWR and the decomposition of
GWR provided by the extended MCT, equation (\ref{eq:full_decomp}). For each panel,
$\delta$ is fixed at the value specified in the upper margin, 
and GWR and components of the decomposition
are plotted against $\eta_2/\eta_1$. The contribution of ATAs ($\Delta_i^{[EC]}$) frequently 
has magnitude comparable to other components, indicating that ATAs can contribute meaningfully
to species coexistence or failure to coexist. In some instances, the GWR line falls 
between the ATA line and the $x$ axis, indicating that, for those parameter values, ATAs make 
the difference between species
coexistence and exclusion of the weaker competitor. These instances, which are shaded, correspond to
ATA rescue or exclusion (Theory). Standard errors of plotted quantities 
were never greater than \Sexpr{round(NA,5)}, so are not displayed. 
%***DAN: Jasmin, we need to replace the NA in the above line by a variable names, which your code should have saved.
%The variable needs to be loaded in the R chunk near the top of this file, and then refereced here, please.
This plot uses $q_{ij}=1$. 
%***DAN: Right, Jasmin?
An analogous plot (SI Fig. \ref{SI-fig:fig4_alt}) was generated 
using $q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. 
%***DAN: Jasmin, I believe the code does not produce the alternate-qij plot yet, but eventually it needs to.
Though results differed in detail, main conclusions were the same.
%***DAN: make sure this is indeed the case once the plot is generated.
}\label{fig:fig4}
\end{figure}

### 2023-02-26 paper/SupMat.Rnw
finished editing REsults for now, though will come back to it again after Jasmin finishes modifying the diatom figures

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig3_qij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig3} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig3} of the main text, but using 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3qij,5)}, so are not displayed. \label{fig:fig3_alt}}
\end{figure}

>>>>

%***DAN: Jasmin, panels d-l of this figure are difficult to read because the y axis extent is such that
%you can't really see what any of the lines are doing except for the ditted and dot-dashed lines. I think we
%need to present 2 versions of the figure, this one and another one. For the other one, the y-axis limits 
%should be determined from the y axis extents of all the lines other than the dotted and dot-dashed lines. 
%Can you please mak this alternative version and let me know when it is made and what the pdf file is, so I 
%insert it? It is possible you will also need two versions of the figure below, but we won't know that 
%until you make that figure.
\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/decompFigLLNqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig3} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig3} of the main text, but using 
$q_{ij}=\exp(\mu_i)/[(1-\delta)\exp(\mu_j)+\delta\exp(\mu_i)]$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(se3qij,5)}, so are not displayed.}\label{fig:fig3_alt}
\end{figure}

%***DAN: The code does not yet produce this figure. Eventually it needs to.
%NOTE: I have assumed this figure will look substantially the same as the corresponding main text 
%figure when I wrote the Results. If it does not, then some revisions will be needed.
\begin{figure}
%\includegraphics[width=\textwidth]{../results_figs/decompFigLBqij.pdf}
\caption[Analogous to Fig. \ref{MT-fig:fig4} but making a different choice for $q_{ij}$]
{Analogous to Fig. \ref{MT-fig:fig4} of the main text, but using 
$q_{ij}=\eta_i/(\eta_j(1-\delta)+\eta_i \delta)$. See the caption of
that figure for details. Standard errors of plotted quantities 
were never greater than \Sexpr{round(0,5)}, so are not displayed.}\label{fig:fig4_alt}
%***DAN: jasmin, once the se is generated and saved by your code, the chunk at the outset of this 
%document needs to be modified to load that quantity, and then the 0 in the above expression 
%needs to be replaced by the variable name used.
\end{figure}
